### 2024-04-14 paper/paper.qmd
Add model set-up to paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: Tam Ly
thanks: "Code and data are available at: [https://github.com/atn-ly/beyonce](https://github.com/atn-ly/beyonce)"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(rstanarm)
library(knitr)
library(here)
library(ggplot2)
library(arrow)
library(scales)
library(modelsummary)
library(marginaleffects)

#Read in data
beyonce_cleaned = read_parquet(
  file = here("data/analysis_data/beyonce_cleaned.parquet"),
  show_col_types = FALSE
)

#Read in model
beyonce_pois <- readRDS(file = here::here("models/beyonce_pois.rds"))
beyonce_nbinom <- readRDS(file = here::here("models/beyonce_nbinom.rds"))

```

# Introduction

# Data {#sec-data}

## Source

## Methodology

## Variables

## Measurement

# Model {#sec-model}

The goal of our modeling strategy is to predict the number of Spotify streams for a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*. We used a negative binomial regression model in a Bayesian framework. Negative binomial regression is a type of generalized linear model that is useful for modeling count data.

## Model set-up

The model that we are interested in is:

\begin{align} 
y_i|\mu_i,r &\sim \mbox{NegBinom}(\mu_i, r) \\
\mbox{log}(\mu_i) &= \alpha + \beta \times \mbox{Number of weeks}_i \\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

Where:

* $y_i$ is the outcome variable, representing the number of Spotify streams for song $i$, 
* $\mu_i$ is a parameter for the negative binomial distribution, representing the probability of success in a single trial,
* $r$ is a parameter for the negative binomial distribution, representing the number of successes,
* $\mbox{Number of weeks}_i$ is the predictor variable, representing the number of weeks spent on the Billboard Hot 100 for song $i$,
* $\alpha$ is a parameter, representing the intercept with a default prior probability distribution that is Normal with a mean of 0 and standard deviation of 2.5,
* $\beta$ is a parameter, representing the slope coefficient with a default prior probability distribution that is Normal with a mean of 0 and standard deviation of 2.5.

## Model justification

```{r}
pp_check(beyonce_pois) +
  theme(legend.position = "bottom")

pp_check(beyonce_nbinom) +
  theme(legend.position = "bottom")
```

# Results {#sec-results}

# Discussion {#sec-discussion}

## First discussion point

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {-}

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

\newpage

# References

### 2024-04-14 paper/paper.qmd
Update model with re-specified priors.

@@
 * $\mbox{Number of weeks}_i$ is the predictor variable, representing the number of weeks spent on the Billboard Hot 100 for song $i$,
-* $\alpha$ is a parameter, representing the intercept with a default prior probability distribution that is Normal with a mean of 0 and standard deviation of 2.5,
+* $\alpha$ is a parameter, representing the intercept with a specified prior probability distribution that is Normal with a mean of 18 and standard deviation of 2.5,
 * $\beta$ is a parameter, representing the slope coefficient with a default prior probability distribution that is Normal with a mean of 0 and standard deviation of 2.5.
@@
 
+We expect a positive relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* based on the positive correlation we observed in the graph in @sec-data.
+
+Negative binomial regression operates under several assumptions. It assumes linearity between the outcome and predictor variables, independence of observations, and no multicollinearity.
+
+We considered Poisson regression as an alternative model since it is also used for count data.
+However, one of the restrictions with Poisson regression is that it assumes equal mean and variance.
+Negative binomial regression relaxes this assumption to allow for over-dispersion.
+We fitted both and compared them using posterior predictive checks in @fig-modelcomparison.
+We see that the negative binomial approach does a better job of fitting the data.
+
+We considered additional model checking and diagnostic issues. Details and graphs can be found in @sec-model-details.
+
 ```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-modelcomparison
+#| layout-ncol: 2
+#| fig-cap: "Comparing posterior prediction checks for Poisson and negative binomial models"
+#| fig-subcap: ["Poisson model", "Negative binomial model"]
+
 pp_check(beyonce_pois) +
@@
 
+In @fig-posteriorvsprior we compare the posterior with the prior.
+@fig-posteriorvsprior-1 suggests that there is an issue with the default prior we specified for $\alpha$.
+Our re-specified model in @fig-posteriorvsprior-2 shows that it does a better job of fitting the data.
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheckandposteriorvsprior
+#| fig-cap: "Comparing the posterior with the prior"
+#| #| fig-subcap: ["Default priors", "Re-specified priors"]
+#| layout-ncol: 2
+
+posterior_vs_prior(beyonce_nbinom_default) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+
+posterior_vs_prior(beyonce_nbinom) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom") +
+  coord_flip()
+```
+
 ## Diagnostics
+
+@fig-diagnostics-1 is a trace plot and it shows that there are no horizontal lines that appear to bounce around and have a nice overlap between the chains. This suggests that there are no problems.
+
+@fig-diagnostics-2 is a Rhat plot and it shows that everything is close to 1 and no more than 1.1. This suggests that there are no problems.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-diagnostics
+#| fig-cap: "Checking the convergence of the MCMC algorithm"
+#| fig-subcap: ["Trace plot", "Rhat plot"]
+#| layout-ncol: 2
+
+plot(beyonce_nbinom, "trace")
+
+plot(beyonce_nbinom, "rhat")
+```
 

### 2024-04-14 scripts/04-model.R

@@ -23,11 +23,21 @@ beyonce_pois <-
     data = beyonce_cleaned,
     family = poisson(link = "log"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 18, scale = 2.5, autoscale = TRUE),
     seed = 302
   )
 
 beyonce_nbinom <-
+  stan_glm(
+    spotify_streams ~ wks_on_chart,
+    data = beyonce_cleaned,
+    family = neg_binomial_2(link = "log"),
+    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 18, scale = 2.5, autoscale = TRUE),
+    seed = 302
+  )
+
+beyonce_nbinom_default <-
   stan_glm(
     spotify_streams ~ wks_on_chart,
     data = beyonce_cleaned,
@@ -46,4 +56,9 @@ saveRDS(
 saveRDS(
   beyonce_nbinom,
   file = "models/beyonce_nbinom.rds"
+)
+
+saveRDS(
+  beyonce_nbinom_default,
+  file = "models/beyonce_nbinom_default.rds"
 )

### 2024-04-14 paper/paper.qmd
Add completed model section to paper

@@
 beyonce_nbinom <- readRDS(file = here::here("models/beyonce_nbinom.rds"))
-
+beyonce_nbinom_default <- readRDS(file = here::here("models/beyonce_nbinom_default.rds"))
 ```
@@
 
-In @fig-posteriorvsprior we compare the posterior with the prior.
+We compare the posterior with the prior.
 @fig-posteriorvsprior-1 suggests that there is an issue with the default prior we specified for $\alpha$.
@@
 #| warning: false
-#| label: fig-ppcheckandposteriorvsprior
+#| label: fig-posteriorvsprior
 #| fig-cap: "Comparing the posterior with the prior"
-#| #| fig-subcap: ["Default priors", "Re-specified priors"]
+#| fig-subcap: ["Default priors", "Re-specified priors"]
 #| layout-ncol: 2

### 2024-04-14 scripts/0-install_packages.R
Add script to install packages

@@ -1,0 +1,18 @@
+#### Preamble ####
+# Purpose: Installs the necessary packages.
+# Author: Tam Ly
+# Date: 18 April 2024
+# Contact: annatn.ly@mail.utoronto.ca
+# Pre-requisites: None
+# Any other information needed? None
+
+install.packages("arrow")
+install.packages("ggplot2")
+install.packages("here")
+install.packages("janitor")
+install.packages("knitr")
+install.packages("marginaleffects")
+install.packages("modelsummary")
+install.packages("rstanarm")
+install.packages("scales")
+install.packages("tidyverse")

### 2024-04-14 scripts/01-download_data.R

@@ -1,26 +1,19 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Author: Tam Ly
+# Date: 18 April 2024
+# Contact: annatn.ly@mail.utoronto.ca
+# Pre-requisites: Run 0-install_packages.R
+# Any other information needed? None
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Download data ####
 # [...ADD CODE HERE TO DOWNLOAD...]
-
-
 
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(the_raw_data, "inputs/data/raw_data.csv") 
-
-         

### 2024-04-14 scripts/02-data_cleaning.R

@@ -3,7 +3,7 @@
 # Author: Tam Ly
 # Date: 18 April 2024
 # Contact: annatn.ly@mail.utoronto.ca
-# Pre-requisites: Run 01-download_data
+# Pre-requisites: Run 01-download_data.R
 # Any other information needed? None
 
 #### Workspace setup ####

### 2024-04-14 scripts/03-test_data.R

@@ -3,7 +3,7 @@
 # Author: Tam Ly
 # Date: 18 April 2024
 # Contact: annatn.ly@mail.utoronto.ca
-# Pre-requisites: Run 02-data_cleaning and 04-model
+# Pre-requisites: Run 02-data_cleaning.R and 04-model.R
 # Any other information needed? None
 
 

### 2024-04-14 paper/paper.qmd
Add data section to paper

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Beyoncé"
 author: Tam Ly
@@
 
-## Source
+## Source and Methodology
 
-## Methodology
+The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@Billboard].
+The data was collected for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs.
+Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@Billboard].
+There were no similar datasets available that could have been used.
+
+We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `kable` [@kable], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], `scales` [@scales], and `tidyverse` [@tidyverse].
 
 ## Variables
+
+There are 4 variables in this dataset:
+
+1. `song` which represents the song titles,
+2. `album` which represents the album titles,
+3. `spotify_streams` which represents the number of Spotify streams, and
+4. `wks_on_chart` which represents the number of weeks spent on the *Billboard Hot 100*.
+
+@tbl-variables shows a sample of the dataset with all the variables and the first 10 out of 140 observations.
+
+```{r}
+#| echo: false
+#| label: tbl-variables
+#| tbl-cap: "Sample of the cleaned dataset with the first 10 observations"
+
+beyonce_cleaned |>
+  slice(1:10) |>
+  kable(
+    col.names = c("Song", "Album", "Spotify Streams", "Weeks on Chart")
+  )
+```
+
+@fig-variables summarizes the data with all 140 observations. We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.
+
+```{r}
+#| echo: false
+#| label: fig-variables
+#| fig-cap: "Relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* for Beyoncé songs"
+
+beyonce_cleaned |>
+  ggplot(mapping = aes(x = wks_on_chart, y = spotify_streams, color = fct_inorder(album))) +
+  geom_point() +
+  theme_minimal() +
+  labs(x = "Weeks on Chart", y = "Spotify Streams", color = "Album")
+```
 
@@
 * $\mbox{Number of weeks}_i$ is the predictor variable, representing the number of weeks spent on the Billboard Hot 100 for song $i$,
-* $\alpha$ is a parameter, representing the intercept with a specified prior probability distribution that is Normal with a mean of 18 and standard deviation of 2.5,
+* $\alpha$ is a parameter, representing the intercept with a specified prior probability distribution that is Normal with a mean of 18 and standard deviation of 2.5, and 
 * $\beta$ is a parameter, representing the slope coefficient with a default prior probability distribution that is Normal with a mean of 0 and standard deviation of 2.5.
@@
 
-We expect a positive relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* based on the positive correlation we observed in the graph in @sec-data.
+We expect a positive relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* based on the positive correlation in the graph that we observed in @sec-data.
 
@@
 
-We considered additional model checking and diagnostic issues. Details and graphs can be found in @sec-model-details.
+We implemented additional model checking and diagnostic issues. Details and graphs can be found in @sec-model-details.
 
@@
 
-@fig-diagnostics-1 is a trace plot and it shows that there are no horizontal lines that appear to bounce around and have a nice overlap between the chains. This suggests that there are no problems.
-
-@fig-diagnostics-2 is a Rhat plot and it shows that everything is close to 1 and no more than 1.1. This suggests that there are no problems.
+@fig-diagnostics-1 is a trace plot and it shows that there are no horizontal lines that appear to bounce around and have a nice overlap between the chains.
+@fig-diagnostics-2 is a Rhat plot and it shows that everything is close to 1 and no more than 1.1.
+This suggests that there are no problems in both.
 

### 2024-04-14 paper/paper.qmd
Add measurement section to paper

@@
 
-The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@Billboard].
+The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@billboard].
 The data was collected for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs.
-Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@Billboard].
+Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@billboard].
 There were no similar datasets available that could have been used.
@@
 
+First, we used Spotify [@spotify] to collect data on Beyoncé albums.
+Here, we had to decide which albums to include in our dataset since Beyoncé has 15 different albums in her Spotify discography.
+We decided to only include her eight studio albums and one soundtrack album and exclude her live albums and compilation albums because these are not as popular.
+Furthermore, among her eight studio albums, we only looked at the deluxe versions, since these contain the same songs with the same streaming numbers as the standard version along with some additional tracks.
+
+Next, using Spotify [@spotify], we collected data on Beyoncé songs from the nine albums we selected and had to decide which types of tracks to include.
+Since we are interested in songs that charted, we decided to exclude remixes, extended mixes, Spanish versions, interludes, and original demos that were included in her albums because these are not as popular.
+Note that we also did not include songs where Beyoncé was a guest feature on another artist’s song.
+
+Then, we used Spotify [@spotify] to collect data on the number of streams for the songs that we selected.
+Spotify gives one stream to a track if it is played for at least 30 seconds and updates its streaming numbers once a day at approximately 3 PM EST [@spotify].
+We collected this data on April 12, 2024 after 3 PM EST.
+
+Lastly, we collected data on the number of weeks each song spent on the *Billboard Hot 100* from Billboard [@billboard].
+Billboard keeps a chart history for Beyoncé that includes the debut date, peak position, peak date, and weeks spent for each song that charted on the *Billboard Hot 100*.
+From this list, we only collected the number of weeks spent on the chart for our selected songs.
+Billboard updates the *Billboard Hot 100* as well as the artist’s chart history every Tuesday [@billboard].
+We collected this data on Friday, April 12, 2024.
+For songs that did not chart, we recorded them with a 0 in our dataset.
+
 # Model {#sec-model}
@@
 \mbox{log}(\mu_i) &= \alpha + \beta \times \mbox{Number of weeks}_i \\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
+\alpha &\sim \mbox{Normal}(18, 2.5) \\
 \beta &\sim \mbox{Normal}(0, 2.5) \\

### 2024-04-14 paper/paper.qmd
Fix some typos in paper

@@
 The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@billboard].
-The data was collected for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs.
+The data was collected by the authors for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs.
 Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@billboard].

### 2024-04-15 paper/paper.qmd
Add figure to results section

@@
   ggplot(mapping = aes(x = wks_on_chart, y = spotify_streams, color = fct_inorder(album))) +
-  geom_point() +
+  geom_point(alpha = 0.5) +
   theme_minimal() +
@@
 
+```{r}
+#| echo: false
+#| label: fig-prediction
+#| fig-cap: "The predicted number of Spotify streams for a Beyoncé song based on the number of weeks spent on the *Billboard Hot 100*"
+
+plot_predictions(beyonce_nbinom, condition = "wks_on_chart") +
+  labs(x = "Weeks on Chart",
+       y = "Spotify Streams") +
+  theme_classic()
+```
+
 # Discussion {#sec-discussion}

### 2024-04-15 paper/paper.qmd
Re-arrange sections in paper
Add table of results

@@
 #| include: false
+#| message: false
 #| warning: false
-#| message: false
 
@@
 library(marginaleffects)
+library(broom.mixed)
 
@@
 
-## Source and Methodology
+## Sources
 
@@
 There were no similar datasets available that could have been used.
-
-We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `kable` [@kable], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], `scales` [@scales], and `tidyverse` [@tidyverse].
-
-## Variables
-
-There are 4 variables in this dataset:
-
-1. `song` which represents the song titles,
-2. `album` which represents the album titles,
-3. `spotify_streams` which represents the number of Spotify streams, and
-4. `wks_on_chart` which represents the number of weeks spent on the *Billboard Hot 100*.
-
-@tbl-variables shows a sample of the dataset with all the variables and the first 10 out of 140 observations.
-
-```{r}
-#| echo: false
-#| label: tbl-variables
-#| tbl-cap: "Sample of the cleaned dataset with the first 10 observations"
-
-beyonce_cleaned |>
-  slice(1:10) |>
-  kable(
-    col.names = c("Song", "Album", "Spotify Streams", "Weeks on Chart")
-  )
-```
-
-@fig-variables summarizes the data with all 140 observations. We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.
-
-```{r}
-#| echo: false
-#| label: fig-variables
-#| fig-cap: "Relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* for Beyoncé songs"
-
-beyonce_cleaned |>
-  ggplot(mapping = aes(x = wks_on_chart, y = spotify_streams, color = fct_inorder(album))) +
-  geom_point(alpha = 0.5) +
-  theme_minimal() +
-  labs(x = "Weeks on Chart", y = "Spotify Streams", color = "Album")
-```
 
@@
 For songs that did not chart, we recorded them with a 0 in our dataset.
+
+## Methodology
+
+We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `kable` [@kable], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], `scales` [@scales], and `tidyverse` [@tidyverse].
+
+## Variables
+
+There are 4 variables in this dataset:
+
+1. `song` which represents the song titles,
+2. `album` which represents the album titles,
+3. `spotify_streams` which represents the number of Spotify streams, and
+4. `wks_on_chart` which represents the number of weeks spent on the *Billboard Hot 100*.
+
+@tbl-variables shows a sample of the dataset with all the variables and the first 10 out of 140 observations.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: tbl-variables
+#| tbl-cap: "Sample of the cleaned dataset with the first 10 observations"
+
+beyonce_cleaned |>
+  slice(1:10) |>
+  kable(
+    col.names = c("Song", "Album", "Spotify Streams", "Weeks on Chart")
+  )
+```
+
+@fig-variables summarizes the data with all 140 observations. We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-variables
+#| fig-cap: "Relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* for Beyoncé songs"
+
+beyonce_cleaned |>
+  ggplot(mapping = aes(x = wks_on_chart, y = spotify_streams, color = fct_inorder(album))) +
+  geom_point(alpha = 0.5) +
+  theme_minimal() +
+  labs(x = "Weeks on Chart", y = "Spotify Streams", color = "Album")
+```
 
@@
 ```{r}
+#| echo: false
 #| eval: true
-#| echo: false
 #| message: false
@@
 
+\newpage
+
 # Results {#sec-results}
@@
 #| echo: false
-#| label: fig-prediction
-#| fig-cap: "The predicted number of Spotify streams for a Beyoncé song based on the number of weeks spent on the *Billboard Hot 100*"
+#| eval: true
+#| message: false
+#| warning: false
+#| label: tbl-results
+#| tbl-cap: "Examining the number of Spotify streams for a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*"
+
+modelsummary(
+  list(
+    "Spotify Streams" = beyonce_nbinom
+  )
+)
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-results
+#| fig-cap: "The predicted number of Spotify streams for a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*"
 

### 2024-04-15 paper/paper.qmd
Fix some minor typos

@@
 
+library(arrow)
+library(broom.mixed)
+library(ggplot2)
+library(here)
+library(knitr)
+library(marginaleffects)
+library(modelsummary)
+library(rstanarm)
 library(tidyverse)
-library(rstanarm)
-library(knitr)
-library(here)
-library(ggplot2)
-library(arrow)
-library(scales)
-library(modelsummary)
-library(marginaleffects)
-library(broom.mixed)
 
@@
 
-We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `kable` [@kable], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], `scales` [@scales], and `tidyverse` [@tidyverse].
+We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], and `tidyverse` [@tidyverse].
 

### 2024-04-15 scripts/0-install_packages.R

@@ -7,6 +7,7 @@
 # Any other information needed? None
 
 install.packages("arrow")
+install.packages("broom.mixed")
 install.packages("ggplot2")
 install.packages("here")
 install.packages("janitor")
@@ -14,5 +15,4 @@ install.packages("knitr")
 install.packages("marginaleffects")
 install.packages("modelsummary")
 install.packages("rstanarm")
-install.packages("scales")
 install.packages("tidyverse")

### 2024-04-15 paper/paper.qmd
Update abstract in paper and README

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper analyzes the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100* utilizing data collected from Spotify and Billboard.
+We find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
+Our discovery highlights the relevance of charts in shaping the music industry."
 format: pdf

### 2024-04-16 paper/paper.qmd
Edit abstract and introduction

@@
 We find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
-Our discovery highlights the relevance of charts in shaping the music industry."
+Our discovery highlights the relevance of charts in shaping today’s music industry."
 format: pdf
@@
 # Introduction
+
+Beyoncé Giselle Knowles-Carter is a singer, songwriter, producer, dancer, and one of the most successful and influential artists of our time.
+Over the course of her career, she has won 32 Grammy Awards, sold more than 200 million records, and 106 of her songs have landed on the *Billboard Hot 100* chart.
+The *Billboard Hot 100* is a music ranking system that showcases 100 of the most popular songs in the United States.
+Although the exact formulas behind its calculation remain unknown to the public, the two main components are radio and song sales.
+Listeners can stream these hits on Spotify.
+With more than 602 million users, it is the world’s most popular audio streaming subscription service.
 

### 2024-04-16 paper/paper.qmd
Edit introduction

--- 2024-04-15 paper/paper.qmd
@@
 # Introduction
+
+Beyoncé Giselle Knowles-Carter is a singer, songwriter, producer, dancer, and one of the most successful and influential artists of our time.
+Over the course of her career, she has won 32 Grammy Awards, sold beyond 200 million records, and more than 100 of her songs have landed on the *Billboard Hot 100* chart.
+The *Billboard Hot 100* is a music ranking system that showcases 100 of the most popular songs in the United States each week.
+Although the exact formula behind its calculation remains unknown to the public, the two main components are radio and song sales.
+Listeners can stream these hits on Spotify, the world’s most popular audio streaming subscription service.
+
+There is a clear gap in knowing what makes a song famous.
+In the ever-changing music industry, it is not only about melody and lyrics, but also promotion.
+In this paper, we look at music promotion and the importance of Billboard charting.
+We analyze the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
+The estimand is the popularity of a Beyoncé song and this is considered in the number of Spotify streams.
 

### 2024-04-16 paper/paper.qmd
Edit introduction in paper

@@
 bibliography: references.bib
-toc: true
 ---
@@
 The *Billboard Hot 100* is a music ranking system that showcases 100 of the most popular songs in the United States each week.
-Although the exact formula behind its calculation remains unknown to the public, the two main components are radio and song sales.
 Listeners can stream these hits on Spotify, the world’s most popular audio streaming subscription service.
@@
 In the ever-changing music industry, it is not only about melody and lyrics, but also promotion.
-In this paper, we look at music promotion and the importance of Billboard charting.
+In this paper, we focus on music promotion and the importance of Billboard charting.
 We analyze the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
 The estimand is the popularity of a Beyoncé song and this is considered in the number of Spotify streams.
+
+Using data collected from Spotify and Billboard, we found that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
+
+The rest of this paper is structured as follows.
+@sec-data provides the sources, measurement, methodology, and variables of the dataset.
+@sec-model provides the model set-up and justification.
+@sec-results provides the results of the model and @sec-discussion provides a discussion of the results.
 
@@
 
-\newpage
-
 # Results {#sec-results}

### 2024-04-17 paper/paper.qmd
Add title to paper and README

@@
 ---
-title: "Beyoncé"
+title: "Do music charts still matter in the streaming age? An analysis predicting Beyoncé’s Spotify numbers using a regression model."
 author: Tam Ly

### 2024-04-17 paper/paper.qmd
Add discussion section in paper

@@
 We find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
-Our discovery highlights the relevance of charts in shaping today’s music industry."
+Our discovery highlights the enduring relevance of charts in shaping today’s music industry."
 format: pdf
@@
 Over the course of her career, she has won 32 Grammy Awards, sold beyond 200 million records, and more than 100 of her songs have landed on the *Billboard Hot 100* chart.
-The *Billboard Hot 100* is a music ranking system that showcases 100 of the most popular songs in the United States each week.
+The *Billboard Hot 100* is a music ranking system that is supposed to showcase 100 of the most popular songs in the United States each week.
 Listeners can stream these hits on Spotify, the world’s most popular audio streaming subscription service.
 
+Do Billboard charts actually reflect which songs are most popular?
 There is a clear gap in knowing what makes a song famous.
@@
 
+\newpage
+
 # Discussion {#sec-discussion}
 
-## First discussion point
+## Findings
 
-## Second discussion point
+In this paper, we collected and visualized data from Spotify and Billboard as discussed in @sec-data.
+Then, we used a Bayesian negative binomial regression model as seen in @sec-model to predict the number of Spotify streams for a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
+Following our analysis in @sec-results, we found that the number of Spotify streams of a Beyoncé song increased as its duration on the *Billboard Hot 100* increased.
+We will now discuss the historical context behind Billboard and why huge superstars, such as Beyoncé, still care about charting.
 
-## Third discussion point
+## A bit of history
+
+In the 1940s, Billboard started developing music charts to try and determine the most popular song.
+This was to help inform people in the music industry, including record stores and jukebox operators, about which records to order.
+The *Billboard Hot 100* was created in 1958 and has undergone complete upheavals since its inception.
+How exactly does Billboard determine the most popular song?
+This has always been the subject of much controversy due to its biased survey methods.
+Billboard first measured sales by surveying record stores, although it was impossible to know if the store clerks were lying or not.
+Then, in a book published in the 1970s, co-founder of Casablanca Records, Larry Harris, alleged that industry insiders had heavy influence over the charts.
+In the 1990s, Billboard began tracking sales based on barcode scans and hip-hop sales seemingly rose dramatically overnight.
+
+Charts are supposed to reflect the industry’s reality and in 2018, it was announced that the *Billboard Hot 100* would take streaming data into account.
+However, the exact formula behind Billboard’s calculations remains unknown to the public.
+We only know that one stream does not necessarily equal one sale and that some streams, such as for on demand services and from paid-tier users, count more than others.
+By the 2010s, the question of what the Billboard charts actually reflect became even more prevalent after rabid fans proved that it was susceptible to coordinated manipulation.
+
+## Why charts still matter
+
+Do artists as big as Beyoncé still care about music charts?
+Chart success can bring significant music promotion to an artist’s career.
+Songs that land on the *Billboard Hot 100* also land on Spotify’s biggest playlists, such as Today’s Top Hits which has almost 35 million followers.
+Cherie Hu, a music industry analyst at the intersection of music and data has deemed playlists “the new album” and “more powerful than radio” [@cherie].
+A placement on Today’s Top Hits can bring up to $163,000 in additional revenue per track.
+Moreover, for new artists, high positions in the charts can lead to more ownership and creative control in their musical career.
+This can help explain the importance of why many of Beyoncé’s longest charting songs come from her earlier albums.
+For more established artists who have a loyal fanbase (even Beyoncé!), charting is essential for maintaining their brand and curtailing any image of a decline.
 
 ## Weaknesses and next steps
+
+Some weaknesses become apparent in our approach in using Spotify streams as a metric for the popularity of a Beyoncé song.
+First, one of Beyoncé’s albums, *Lemonade*, was added to Spotify three years after its release.
+This means that the number of Spotify streams for the songs from this album are underrepresented in our dataset.
+Furthermore, Spotify numbers are also not immune to industry politics that underlie promotional mechanics.
+For example, all of the major record labels own a sizable share of Spotify and can give some artists preferential treatment on the platform.
+
+In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album released on March 29, 2024, *COWBOY CARTER*, more time to see how long it lasts on the chart.
+Another possible idea for future work could be to use a different
 

### 2024-04-17 paper/paper.qmd
Update written sections in paper

--- 2024-04-17 paper/paper.qmd
@@
 date-format: long
-abstract: "This paper analyzes the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100* utilizing data collected from Spotify and Billboard.
-We find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
-Our discovery highlights the relevance of charts in shaping today’s music industry."
+abstract: "Music charts are a powerful marketing tool.
+This paper analyzes the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100* utilizing data collected from Spotify and Billboard.
+In our negative binomial regression model, we find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
+Our discovery highlights the relevance of charts in shaping today’s music business industry."
 format: pdf
@@
 Beyoncé Giselle Knowles-Carter is a singer, songwriter, producer, dancer, and one of the most successful and influential artists of our time.
-Over the course of her career, she has won 32 Grammy Awards, sold beyond 200 million records, and more than 100 of her songs have landed on the *Billboard Hot 100* chart.
-The *Billboard Hot 100* is a music ranking system that showcases 100 of the most popular songs in the United States each week.
-Listeners can stream these hits on Spotify, the world’s most popular audio streaming subscription service.
+Over the course of her career, she has won 32 Grammy Awards, sold beyond 200 million records, and more than 100 of her songs have landed on the *Billboard Hot 100* chart [@sony].
+The *Billboard Hot 100* is a music ranking system that is supposed to showcase 100 of the most popular songs in the United States each week [@substack].
+Listeners can stream these hits on Spotify, the world’s most popular audio streaming subscription service [@aboutspotify].
 
@@
 In the ever-changing music industry, it is not only about melody and lyrics, but also promotion.
-In this paper, we focus on music promotion and the importance of Billboard charting.
+In this paper, we focus on music promotion and the importance of Billboard charting as a marketing tool.
 We analyze the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
@@
 
-Using data collected from Spotify and Billboard, we found that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
+We are consequently able to answer the following question: What is the effect of longevity on the Billboard charts on a Beyoncé song’s number of Spotify streams?
+Using data collected from Spotify and Billboard and a negative binomial regression model, we found that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases.
+We deduce that Billboard charting is still important for an artists’ popularity and career.
 
@@
 The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@billboard].
-The data was collected by the authors for the purpose of this paper to investigate the number of Spotify streams based on weeks spent on the *Billboard Hot 100* for Beyoncé songs.
-Song titles, album titles, and the number of Spotify streams were collected from Spotify [@spotify], while weeks spent on the *Billboard Hot 100* were collected from Billboard [@billboard].
+The data was collected by the authors for the purpose of this paper to investigate the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
+Song titles, album titles, and the number of Spotify streams were collected from Spotify, while weeks spent on the *Billboard Hot 100* were collected from Billboard.
 There were no similar datasets available that could have been used.
@@
 
-First, we used Spotify [@spotify] to collect data on Beyoncé albums.
+First, we used Spotify to collect data on Beyoncé albums.
 Here, we had to decide which albums to include in our dataset since Beyoncé has 15 different albums in her Spotify discography.
-We decided to only include her eight studio albums and one soundtrack album and exclude her live albums and compilation albums because these are not as popular.
+We decided to only include her eight studio albums and one soundtrack album and exclude her live albums and compilation albums because these did not chart.
 Furthermore, among her eight studio albums, we only looked at the deluxe versions, since these contain the same songs with the same streaming numbers as the standard version along with some additional tracks.
 
-Next, using Spotify [@spotify], we collected data on Beyoncé songs from the nine albums we selected and had to decide which types of tracks to include.
+Next, using Spotify, we collected data on Beyoncé songs from the nine albums we selected and had to decide which types of tracks to include.
 Since we are interested in songs that charted, we decided to exclude remixes, extended mixes, Spanish versions, interludes, and original demos that were included in her albums because these are not as popular.
@@
 
-Then, we used Spotify [@spotify] to collect data on the number of streams for the songs that we selected.
-Spotify gives one stream to a track if it is played for at least 30 seconds and updates its streaming numbers once a day at approximately 3 PM EST [@spotify].
+Then, we used Spotify to collect data on the number of streams for the songs that we selected.
+Spotify gives one stream to a track if it is played for at least 30 seconds and updates its streaming numbers once a day at approximately 3 PM EST.
 We collected this data on April 12, 2024 after 3 PM EST.
 
-Lastly, we collected data on the number of weeks each song spent on the *Billboard Hot 100* from Billboard [@billboard].
+Lastly, we collected data on the number of weeks each song spent on the *Billboard Hot 100* from Billboard.
 Billboard keeps a chart history for Beyoncé that includes the debut date, peak position, peak date, and weeks spent for each song that charted on the *Billboard Hot 100*.
 From this list, we only collected the number of weeks spent on the chart for our selected songs.
-Billboard updates the *Billboard Hot 100* as well as the artist’s chart history every Tuesday [@billboard].
+Billboard updates the *Billboard Hot 100* as well as the artist’s chart history every Tuesday.
 We collected this data on Friday, April 12, 2024.
@@
 
-There are 4 variables in this dataset:
+There are 4 variables in the dataset that we created:
 
@@
 
+To visualize our data, we create a table and graph.
 @tbl-variables shows a sample of the dataset with all the variables and the first 10 out of 140 observations.
+Furthermore, @fig-variables show a scatterplot of the data with all 140 observations.
+We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.
 
@@
 ```
-
-@fig-variables summarizes the data with all 140 observations. We see a positive correlation between the number of Spotify streams and weeks spent on the *Billboard Hot 100*.
 
@@
 
-The goal of our modeling strategy is to predict the number of Spotify streams for a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
+The goal of our modeling strategy is to predict the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
 We used a negative binomial regression model in a Bayesian framework.
@@
 
-We expect a positive relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* based on the positive correlation in the graph that we observed in @sec-data.
+We expect a positive relationship between the number of Spotify streams and weeks spent on the *Billboard Hot 100* based on the positive correlation in the scatterplot graph that we observed in @sec-data.
 
-Negative binomial regression operates under several assumptions. It assumes linearity between the outcome and predictor variables, independence of observations, and no multicollinearity.
+Negative binomial regression operates under several assumptions.
+It assumes linearity between the outcome and predictor variables, independence of observations, and no multicollinearity [@negativebinomial].
 
@@
 # Results {#sec-results}
+
+@tbl-results demonstrates what was expected: the positive number 0.094 means that there is a positive relationship between the number of Spotify streams of a Beyoncé song and the number of weeks it spent on the *Billboard Hot 100*.
+@fig-results further illustrates this and makes it clear that we expect a positive relationship.
 
@@
 
-## First discussion point
+## Findings
 
-## Second discussion point
+In this paper, we collected and visualized data from Spotify and Billboard as discussed in @sec-data.
+Then, we used a Bayesian negative binomial regression model as seen in @sec-model to predict the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
+Following our analysis in @sec-results, we found that the number of Spotify streams of a Beyoncé song increased as its duration on the *Billboard Hot 100* increased.
+We will now discuss the historical context behind Billboard and why huge superstars, such as Beyoncé, still care about charting.
 
-## Third discussion point
+## A bit of history
+
+In the 1940s, Billboard started developing music charts to try and determine the most popular song [@substack].
+This was to help inform people in the music industry, including record stores and jukebox operators, about which records to order [@substack].
+The *Billboard Hot 100* was created in 1958 and has undergone complete upheavals since its inception [@substack].
+How exactly does Billboard determine the most popular song?
+This has always been the subject of much controversy due to its biased survey methods.
+Billboard first measured sales by surveying record stores, although it was impossible to know if the store clerks were lying or not [@substack].
+Then, co-founder of Casablanca Records, Larry Harris, alleged that industry insiders had heavy influence over the charts [@substack].
+In the 1990s, Billboard began tracking sales based on barcode scans and hip-hop sales seemingly rose dramatically overnight [@substack].
+
+Charts are supposed to reflect the industry’s reality and in 2018, it was announced that the *Billboard Hot 100* would take streaming data into account [@substack].
+However, the exact formula behind Billboard’s calculations remains unknown to the public.
+We only know that one stream does not necessarily equal one sale and that some streams, such as for on demand services and from paid-tier users, count more than others [@substack].
+By the 2010s, the question of what the Billboard charts actually reflect became even more prevalent after fans proved that it was susceptible to coordinated manipulation [@substack].
+
+## Why charts still matter
+
+Do artists as big as Beyoncé still care about music charts?
+Chart success can bring significant music promotion to an artist’s career.
+Songs that land on the *Billboard Hot 100* also land on Spotify’s biggest playlists, such as Today’s Top Hits which has almost 35 million followers [@todaystophits].
+Cherie Hu, a music industry analyst at the intersection of music and data, has deemed playlists “the new album” and “more powerful than radio” as a placement on Today’s Top Hits can bring up to $163,000 in additional revenue per track [@cherie].
+Moreover, for new artists, high positions in the charts can lead to more ownership and creative control in their musical career.
+This can help explain the importance of why many of Beyoncé’s longest charting songs come from her earlier albums.
+For more established artists who have a loyal fanbase, charting is essential for maintaining their brand and curtailing any image of a decline.
 
 ## Weaknesses and next steps
+
+Some weaknesses become apparent in our approach in using Spotify streams as a metric for the popularity of a Beyoncé song.
+First, one of Beyoncé’s albums, *Lemonade*, was added to Spotify three years after its release.
+This means that the number of Spotify streams for the songs from this album are underrepresented in our dataset.
+Furthermore, Spotify numbers are also not immune to industry politics that underlie promotional mechanics.
+All of the major record labels own a sizable share of Spotify and can give some artists preferential treatment on the platform.
+For example, Beyoncé is under Sony Music which owns a 2.65% stake in Spotify [@owners].
+Lastly, we did not consider that Beyoncé’s older songs have had more time to accumulate streams than her latest work.
+For instance, *COWBOY CARTER* was just released on March 29, 2024 while *Dangerously in Love* was released on June 20, 2003 [@spotify].
+
+In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album *COWBOY CARTER* more time to see how long it lasts on the chart.
+We could also standardize the length to accumulate streams such as one year after its release for consistency.
+Another possible idea for future work could be to use a mix of new and established artists to see if we get the same result.
 

### 2024-04-18 paper/paper.qmd
Add completed references to paper

@@
 To visualize our data, we create a table and graph.
-@tbl-variables shows a sample of the dataset with all the variables and the first 10 out of 140 observations.
+@tbl-variables shows a sample of the dataset with all the variables and the first 5 out of 140 observations.
 Furthermore, @fig-variables show a scatterplot of the data with all 140 observations.
@@
 #| label: tbl-variables
-#| tbl-cap: "Sample of the cleaned dataset with the first 10 observations"
+#| tbl-cap: "Sample of the cleaned dataset with the first 5 observations"
 
 beyonce_cleaned |>
-  slice(1:10) |>
+  slice(1:5) |>
   kable(
@@
 
-In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album *COWBOY CARTER* more time to see how long it lasts on the chart.
+In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album, *COWBOY CARTER*, more time to see how long it lasts on the chart.
 We could also standardize the length to accumulate streams such as one year after its release for consistency.

### 2024-04-18 other/datasheet/datasheet_template.qmd
Update information in the datasheet

---
title: "Datasheet for the Beyoncé dataset"
author: Tam Ly
thanks: "Code and data are available at: [https://github.com/atn-ly/beyonce](https://github.com/atn-ly/beyonce)"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to investigate the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*. There were no similar datasets available that could have been used.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Me.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - No funding was received.
4. *Any other comments?*
    - No.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances that comprise the dataset represent Beyoncé songs.
2. *How many instances are there in total (of each type, if appropriate)?*
	- 140.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is a sample of Beyoncé songs from 9 out of 15 of her albums. The sample is representative of her songs that have charted on the *Billboard Hot 100*.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance constists of the song title, album title, number of Spotify streams, and number of weeks it spent on the *Billboard Hot 100*.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- No.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- There are no relationships between instances.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- No.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- It is self-contained.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No.
16. *Any other comments?*
	- No.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- Each instance was directly observable from Spotify and Billboard.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- I collected the numbers from the Spotify and Billboard websites.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- N/A
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Me.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- It took me about an hour on April 12, 2024.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- I collected the numbers from the Spotify and Billboard websites.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- N/A
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- N/A
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- N/A
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A
12. *Any other comments?*
	- No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- No.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- No.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- No.
4. *Any other comments?*
	- No.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- No.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No.
3. *What (other) tasks could the dataset be used for?*
	- None.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No.
6. *Any other comments?*
	- No.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- No.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- No.
3. *When will the dataset be distributed?*
	- No.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No.
7. *Any other comments?*
	- No.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Me.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Email me.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- No.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- No.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- No.
8. *Any other comments?*
	- No.

\newpage

# References

### 2024-04-18 scripts/01-download_data.R
Rename scripts after deleting download_data.R

@@ -1,19 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Tam Ly
-# Date: 18 April 2024
-# Contact: annatn.ly@mail.utoronto.ca
-# Pre-requisites: Run 0-install_packages.R
-# Any other information needed? None
-
-
-#### Workspace setup ####
-library(tidyverse)
-
-#### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
-#### Save data ####
-# [...UPDATE THIS...]
-# change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 

### 2024-04-18 paper/paper.qmd
Add more references to paper
Fix a minor typo in paper
Fix minor typos and edit prose for final submission

@@
 The dataset used in this paper was created using data gathered from Spotify [@spotify] and Billboard [@billboard].
-The data was collected by the authors for the purpose of this paper to investigate the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
+The data was collected by the author for the purpose of this paper to investigate the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100*.
 Song titles, album titles, and the number of Spotify streams were collected from Spotify, while weeks spent on the *Billboard Hot 100* were collected from Billboard.
@@
 We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], and `tidyverse` [@tidyverse].
+The code used in our analysis was adapted from *Telling Stories with Data* [@rohan].
 
@@
 \alpha &\sim \mbox{Normal}(18, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
+\beta &\sim \mbox{Normal}(0, 2.5)
 \end{align}
@@
 By the 2010s, the question of what the Billboard charts actually reflect became even more prevalent after fans proved that it was susceptible to coordinated manipulation [@substack].
+Due to its ambiguity, we consider the effect of Billboard charts on a song’s popularity rather than what they represent.
 
@@
 Chart success can bring significant music promotion to an artist’s career.
-Songs that land on the *Billboard Hot 100* also land on Spotify’s biggest playlists, such as Today’s Top Hits which has almost 35 million followers [@todaystophits].
-Cherie Hu, a music industry analyst at the intersection of music and data, has deemed playlists “the new album” and “more powerful than radio” as a placement on Today’s Top Hits can bring up to $163,000 in additional revenue per track [@cherie].
+Songs that land on the *Billboard Hot 100* also land on Spotify’s biggest playlists, such as *Today’s Top Hits* which has almost 35 million followers [@todaystophits].
+Cherie Hu, a music industry analyst at the intersection of music and data, has deemed playlists “the new album” and “more powerful than radio” as a placement on *Today’s Top Hits* can bring up to $163,000 in additional revenue per track [@cherie].
+
 Moreover, for new artists, high positions in the charts can lead to more ownership and creative control in their musical career.
@@
 This means that the number of Spotify streams for the songs from this album are underrepresented in our dataset.
-Furthermore, Spotify numbers are also not immune to industry politics that underlie promotional mechanics.
+
+Furthermore, Spotify numbers are not immune to industry politics that underlie promotional mechanics.
 All of the major record labels own a sizable share of Spotify and can give some artists preferential treatment on the platform.
 For example, Beyoncé is under Sony Music which owns a 2.65% stake in Spotify [@owners].
-Lastly, we did not consider that Beyoncé’s older songs have had more time to accumulate streams than her latest work.
-For instance, *COWBOY CARTER* was just released on March 29, 2024 while *Dangerously in Love* was released on June 20, 2003 [@spotify].
 
-In the future, it could be on interest to run the analysis again to give Beyoncé’s latest album, *COWBOY CARTER*, more time to see how long it lasts on the chart.
-We could also standardize the length to accumulate streams such as one year after its release for consistency.
+Lastly, we did not consider that Spotify counts repeated streams and that Beyoncé’s older songs have had more time to accumulate streams.
+For instance, *COWBOY CARTER* was recently released on March 29, 2024 while *Dangerously in Love* was released on June 20, 2003 [@spotify].
+
+In the future, it could be of interest to run the analysis again to give Beyoncé’s latest album, *COWBOY CARTER*, more time to see how long it lasts on the chart.
+We could also standardize the length of time to accumulate streams, such as one year after its release, for consistency.
 Another possible idea for future work could be to use a mix of new and established artists to see if we get the same result.

### 2024-04-18 scripts/00-install_packages.R
Add comments to code for each script

@@ -6,6 +6,7 @@
 # Pre-requisites: None
 # Any other information needed? None
 
+
 install.packages("arrow")
 install.packages("broom.mixed")
 install.packages("ggplot2")

### 2024-04-18 scripts/01-simulate_data.R

@@ -3,28 +3,33 @@
 # Author: Tam Ly
 # Date: 18 April 2024
 # Contact: annatn.ly@mail.utoronto.ca
-# Pre-requisites: Run 000-install_packages
+# Pre-requisites: Run 00-install_packages
 # Any other information needed? None
 
 
 #### Workspace setup ####
 library(tidyverse)
 
+
 #### Simulate data ####
+#Set seed for reproducibility
 set.seed(302)
 
+#Create simulated dataset
 beyonce_simulation <-
   tibble(
     number_weeks_on_chart = runif(min = 0, max = 20, n = 100) |> round(0),
     number_streams = rpois(n = 100, lambda = 15)
   )
 
+#Change class of number_week_on_chart to integer
 beyonce_simulation <-
   beyonce_simulation |> 
   mutate(
     number_weeks_on_chart = as.integer(number_weeks_on_chart)
     )
 
+#Create a scatterplot of simulated dataset
 beyonce_simulation |>
   ggplot(aes(y = number_streams, x = number_weeks_on_chart)) +
   geom_point() +
@@ -34,6 +39,7 @@ beyonce_simulation |>
   ) +
   theme_classic() +
   scale_fill_brewer(palette = "Set1")
+
 
 #### Test simulated data ####
 #Tests of class:

### 2024-04-18 scripts/02-data_cleaning.R

@@ -3,17 +3,21 @@
 # Author: Tam Ly
 # Date: 18 April 2024
 # Contact: annatn.ly@mail.utoronto.ca
-# Pre-requisites: Run 01-download_data.R
+# Pre-requisites: None
 # Any other information needed? None
+
 
 #### Workspace setup ####
 library(tidyverse)
 library(janitor)
 library(arrow)
 
+
 #### Clean data ####
+#Read in raw data
 beyonce_raw <- read_csv("data/raw_data/beyonce_raw.csv")
 
+#Clean column names using janitor and change classes to integer
 beyonce_cleaned <-
   beyonce_raw |>
   clean_names() |> 
@@ -21,6 +25,7 @@ beyonce_cleaned <-
     spotify_streams = as.integer(spotify_streams),
     wks_on_chart = as.integer(wks_on_chart)
   )
+
 
 #### Save data ####
 write_parquet(beyonce_cleaned, "data/analysis_data/beyonce_cleaned.parquet")

### 2024-04-18 scripts/03-test_data.R

@@ -15,9 +15,11 @@ library(arrow)
 #### Read data ####
 beyonce_cleaned <- read_parquet("data/analysis_data/beyonce_cleaned.parquet")
 
+
 #### Read model ####
 beyonce_pois <- readRDS(file = here::here("models/beyonce_pois.rds"))
 beyonce_nbinom <- readRDS(file = here::here("models/beyonce_nbinom.rds"))
+
 
 #### Test data ####
 #Tests of class:

### 2024-04-18 scripts/04-model.R

@@ -13,8 +13,10 @@ library(tidyverse)
 library(rstanarm)
 library(arrow)
 
+
 #### Read data ####
 beyonce_cleaned <- read_parquet("data/analysis_data/beyonce_cleaned.parquet")
+
 
 ### Model data ####
 beyonce_pois <-
@@ -46,6 +48,7 @@ beyonce_nbinom_default <-
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     seed = 302
   )
+
 
 #### Save model ####
 saveRDS(

### 2024-04-18 scripts/00-install_packages.R
Style and lint the code in each script

@@ -13,7 +13,9 @@ install.packages("ggplot2")
 install.packages("here")
 install.packages("janitor")
 install.packages("knitr")
+install.packages("lintr")
 install.packages("marginaleffects")
 install.packages("modelsummary")
 install.packages("rstanarm")
+install.packages("styler")
 install.packages("tidyverse")

### 2024-04-18 scripts/01-simulate_data.R

@@ -1,5 +1,6 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of number of Spotify streams and number of weeks on the Billboard Hot 100.
+# Purpose: Simulates a dataset of number of Spotify streams and number of
+# weeks on the Billboard Hot 100.
 # Author: Tam Ly
 # Date: 18 April 2024
 # Contact: annatn.ly@mail.utoronto.ca
@@ -9,27 +10,30 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(lintr)
+library(styler)
+library(here)
 
 
 #### Simulate data ####
-#Set seed for reproducibility
+# Set seed for reproducibility
 set.seed(302)
 
-#Create simulated dataset
+# Create simulated dataset
 beyonce_simulation <-
   tibble(
     number_weeks_on_chart = runif(min = 0, max = 20, n = 100) |> round(0),
     number_streams = rpois(n = 100, lambda = 15)
   )
 
-#Change class of number_week_on_chart to integer
+# Change class of number_week_on_chart to integer
 beyonce_simulation <-
-  beyonce_simulation |> 
+  beyonce_simulation |>
   mutate(
     number_weeks_on_chart = as.integer(number_weeks_on_chart)
-    )
+  )
 
-#Create a scatterplot of simulated dataset
+# Create a scatterplot of simulated dataset
 beyonce_simulation |>
   ggplot(aes(y = number_streams, x = number_weeks_on_chart)) +
   geom_point() +
@@ -42,12 +46,16 @@ beyonce_simulation |>
 
 
 #### Test simulated data ####
-#Tests of class:
+# Tests of class:
 beyonce_simulation$number_weeks_on_chart |> class() == "integer"
 beyonce_simulation$number_streams |> class() == "integer"
 
-#Tests of number of observations:
+# Tests of number of observations:
 beyonce_simulation$number_weeks_on_chart |> min() >= 0
 beyonce_simulation$number_weeks_on_chart |> max() <= 52
 beyonce_simulation$number_streams |> min() >= 1
 beyonce_simulation$number_streams |> max() <= 2000
+
+#### Style code ####
+lint(filename = here("scripts/01-simulate_data.R"))
+style_file(path = here("scripts/01-simulate_data.R"))

### 2024-04-18 scripts/02-data_cleaning.R

@@ -11,16 +11,19 @@
 library(tidyverse)
 library(janitor)
 library(arrow)
+library(lintr)
+library(styler)
+library(here)
 
 
 #### Clean data ####
-#Read in raw data
+# Read in raw data
 beyonce_raw <- read_csv("data/raw_data/beyonce_raw.csv")
 
-#Clean column names using janitor and change classes to integer
+# Clean column names using janitor and change classes to integer
 beyonce_cleaned <-
   beyonce_raw |>
-  clean_names() |> 
+  clean_names() |>
   mutate(
     spotify_streams = as.integer(spotify_streams),
     wks_on_chart = as.integer(wks_on_chart)
@@ -29,3 +32,8 @@ beyonce_cleaned <-
 
 #### Save data ####
 write_parquet(beyonce_cleaned, "data/analysis_data/beyonce_cleaned.parquet")
+
+
+#### Style code ####
+lint(filename = here("scripts/02-data_cleaning.R"))
+style_file(path = here("scripts/02-data_cleaning.R"))

### 2024-04-18 scripts/03-test_data.R

@@ -10,6 +10,9 @@
 #### Workspace setup ####
 library(tidyverse)
 library(arrow)
+library(lintr)
+library(styler)
+library(here)
 
 
 #### Read data ####
@@ -22,17 +25,23 @@ beyonce_nbinom <- readRDS(file = here::here("models/beyonce_nbinom.rds"))
 
 
 #### Test data ####
-#Tests of class:
+# Tests of class:
 beyonce_cleaned$wks_on_chart |> class() == "integer"
 beyonce_cleaned$spotify_streams |> class() == "integer"
 
-#Tests of number of observations:
+# Tests of number of observations:
 beyonce_cleaned$wks_on_chart |> min() >= 0
 beyonce_cleaned$wks_on_chart |> max() <= 52
 beyonce_cleaned$spotify_streams |> min() >= 1
 beyonce_cleaned$spotify_streams |> max() <= 2000000000
 
+
 #### Test model ####
-#Tests of coefficients
+# Tests of coefficients
 between(beyonce_pois$coefficients[1], 0, 20)
 between(beyonce_pois$coefficients[2], 0, 20)
+
+
+#### Style code ####
+lint(filename = here("scripts/03-test_data.R"))
+style_file(path = here("scripts/03-test_data.R"))

### 2024-04-18 scripts/04-model.R

@@ -1,5 +1,6 @@
 #### Preamble ####
-# Purpose: Models number of Spotify streams based on number of weeks on the Billboard Hot 100.
+# Purpose: Models number of Spotify streams based on number of weeks on the
+# Billboard Hot 100.
 # Author: Tam Ly
 # Date: 18 April 2024
 # Contact: annatn.ly@mail.utoronto.ca
@@ -12,6 +13,9 @@
 library(tidyverse)
 library(rstanarm)
 library(arrow)
+library(lintr)
+library(styler)
+library(here)
 
 
 #### Read data ####
@@ -65,3 +69,8 @@ saveRDS(
   beyonce_nbinom_default,
   file = "models/beyonce_nbinom_default.rds"
 )
+
+
+#### Style code ####
+lint(filename = here("scripts/04-model.R"))
+style_file(path = here("scripts/04-model.R"))

### 2024-04-18 paper/paper.qmd
Update references with lintr and styler

@@
 
-We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `knitr` [@knitr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], and `tidyverse` [@tidyverse].
+We analyzed the data in R [@citeR] using the following packages: `arrow` [@arrow], `broom.mixed` [@broommixed], `ggplot2` [@ggplot2], `here` [@here], `janitor` [@janitor], `knitr` [@knitr], `lintr` [@lintr], `marginaleffects` [@marginaleffects], `modelsummary` [@modelsummary], `rstanarm` [@rstanarm], `styler` [@styler], and `tidyverse` [@tidyverse].
 The code used in our analysis was adapted from *Telling Stories with Data* [@rohan].
